---
title: "DJIA Collaborative Debugging Project"
author: "Workshop Team"
date: "2026-07-15"
output:
  html_document:
    toc: true
    toc_depth: 2
---

# Welcome

This parent document stitches together many child files.
Each student should edit only their assigned file first.
The goal is to pull historical stock/dividend data, clean it, compute performance, and rank companies.

## Notes For Students

- The project is intentionally messy.
- Some objects are named inconsistently on purpose.
- Some child files contain small bugs to fix.

```{r project_setup, include=TRUE}
    # This chunk is only to set global chunk options and print project notes.
 # Keep warnings/messages visible so students can spot package/data issues quickly.
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)

   cat("Starting DJIA collaborative report...\n")
```

## Run Child Files In Order

```{r child_01}
 # Stage 1: setup + ingestion (file order matters for object dependencies).
    knitr::knit_child("01_setup_libs.Rmd")
```

```{r child_02}
    # Pull tech and communication names.
    knitr::knit_child("02_get_data_tech.Rmd")
```

```{r child_03}
      # Pull finance and payment names.
    knitr::knit_child("03_get_data_finance.Rmd")
```

```{r child_04}
 # Pull retail/consumer names (this child is a .md file intentionally).
    knitr::knit_child("04_get_data_retail_consumer.md")
```

```{r child_05}
    # Pull healthcare names.
    knitr::knit_child("05_get_data_health.Rmd")
```

```{r child_06}
      # Pull industrial/energy/materials names.
    knitr::knit_child("06_get_data_industrials.Rmd")
```

```{r child_07}
 # Stage 2 merge.
    knitr::knit_child("07_merge_data.Rmd")
```

```{r child_08}
    # Stage 2 clean prices.
    knitr::knit_child("08_clean_prices.Rmd")
```

```{r child_09}
      # Stage 2 clean dividends.
    knitr::knit_child("09_clean_dividends.Rmd")
```

```{r child_10}
 # Stage 3 compute 1-year stock metrics.
    knitr::knit_child("10_calc_1yr_stock.Rmd")
```

```{r child_11}
    # Stage 3 compute 5-year stock metrics.
    knitr::knit_child("11_calc_5yr_stock.Rmd")
```

```{r child_12}
      # Stage 3 compute 10-year stock metrics.
    knitr::knit_child("12_calc_10yr_stock.Rmd")
```

```{r child_13}
 # Stage 4 compute 1-year dividend metrics.
    knitr::knit_child("13_calc_1yr_div.Rmd")
```

```{r child_14}
    # Stage 4 compute 5-year dividend metrics.
    knitr::knit_child("14_calc_5yr_div.Rmd")
```

```{r child_15}
      # Stage 4 compute 10-year dividend metrics.
    knitr::knit_child("15_calc_10yr_div.Rmd")
```

```{r child_16}
 # Stage 5 rank stock performance.
    knitr::knit_child("16_rank_stock_perf.Rmd")
```

```{r child_17}
    # Stage 5 rank dividend performance.
    knitr::knit_child("17_rank_div_perf.Rmd")
```

```{r child_18}
      # Stage 5 merge all ranking outputs.
    knitr::knit_child("18_merge_rankings.Rmd")
```

```{r child_19}
 # Stage 6 plot stock leaders/laggards.
    knitr::knit_child("19_plot_top_stocks.Rmd")
```

```{r child_20}
    # Stage 6 plot top dividend growers.
    knitr::knit_child("20_plot_top_divs.Rmd")
```

```{r child_21}
      # Stage 6 final summary table/report.
    knitr::knit_child("21_summary_report.Rmd")
```
